Lexicalized Domain Representations for Neural Machine Translation

### 2019-08-27 2019/iwslt/submission.tex
additional domain scenario

\begin{table}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|c|}
\hline
Model & EMEA & EPPS & ECB & Avg. \\
\hline
%\multicolumn{8}{l}{} \\[-9pt]  
\multicolumn{5}{l}{English$\rightarrow$French} \\
\hline
$\mathtt{Mixed}$          & 67.69$_{47.60}$ & 37.50 & 53.49 & \\
\hline
$\mathtt{FT}_{EMEA}$ & 76.77$_{49.43}$ & 17.16 & 11.99 &\\
$\mathtt{FT}_{EPPS}$  & 20.86 & 37.04 & 24.53 &  \\
$\mathtt{FT}_{ECB}$    & 26.93 & 27.09 & 56.52 & \\
\hline
$\mathtt{DC}$              & 67.87$_{45.42}$ & 37.31 & 54.14 & \\
\hline
$\mathtt{LDR}_{oracle}$            & 74.26$_{49.90}$ & 37.67 & 54.07 & \\
$\mathtt{LDR}_{oracle}^{0.5}$   & 74.95$_{49.38}$ & 37.35 & 55.91 & \\
%$\mathtt{LDR}_{generic}$          & 73.97$_{49.54}$ & 37.81 & 53.67 & \\
$\mathtt{LDR}_{pred}$               & 74.29 $_{49.84}$ & 37.73 & 54.01 & \\
$\mathtt{LDR}_{wrong}$            & 72.95$_{49.78}$ & 37.62 & 53.35 & \\
  \hline
%\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{5}{l}{English$\rightarrow$German} \\
\hline
$\mathtt{Mixed}$         & 64.57$_{42.99}$ & 26.47 & 68.67 & \\
\hline
$\mathtt{FT}_{EMEA}$ & 68.35$_{42.97}$ & 17.02 & 32.87 & \\
$\mathtt{FT}_{EPPS}$  & 36.19 & 26.29 & 40.71 & \\
$\mathtt{FT}_{ECB}$   & 24.72 & 18.36 & 74.05 & \\
\hline
$\mathtt{DC}$ & 63.48$_{42.98}$ & 26.27 & 66.95 & \\
\hline
$\mathtt{LDR}_{oracle}$ & 70.90$_{46.12}$ & 26.30 & 68.90 & \\
$\mathtt{LDR}_{oracle}^{0.5}$ & 71.31$_{45.23}$ & 25.98 & 73.74 & \\
%$\mathtt{LDR}_{generic}$ & 70.86$_{45.60}$ & 26.14 & 68.59 & \\
$\mathtt{LDR}_{pred}$ & 70.89$_{46.12}$ & 26.53 & 68.63 & \\
$\mathtt{LDR}_{wrong}$ & 69.51$_{43.50}$ & 26.31 & 66.86 & \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BLEU scores for  Transformer systems \label{tab:results-trsf}}
\end{table}

\begin{table}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|c|}
\hline
Model & EMEA & EPPS & ECB & Avg. \\
\hline
%\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{5}{l}{English$\rightarrow$French} \\
\hline
$Mixed$                         & 65.42$_{45.11}$ & 34.70 & 51.38 & \\
\hline
$\mathtt{FT}_{EMEA}$   & 72.06$_{47.33}$ & 18.62 & 16.78 & \\
$\mathtt{FT}_{EPPS}$    & 35.47 $ $ & 34.61 & 39.56 & \\
$\mathtt{FT}_{ECB}$      & 21.93 $ $ & 22.60 & 51.53 & \\
\hline
$\mathtt{DC}$                            & 68.26 $_{43.76}$ & 35.13 & 50.09 & \\
% \hline
%$\mathtt{WDCMT}$           & 68.76 $_{45.29}$ & 35.71 & 52.75 & \\
\hline
$\mathtt{LDR}_{oracle}$            & 71.73 $_{46.30}$ & 35.21 & 50.91 & \\
%$\mathtt{LDR_{condgru}}_{pred}$   & 71.7 $_{46.21}$ & 35.09 & 51.22 & \\
$\mathtt{LDR}_{oracle}^{0.5}$   & 71.70$_{46.41}$ & 34.24& 52.37 & \\
%$\mathtt{LDR}_{generic}$          & 70.59 $_{46.37}$ & 35.22 & 49.68 & \\
$\mathtt{LDR}_{pred}$               & 72.76 $_{46.35}$ & 35.10 & 50.38 & \\
$\mathtt{LDR}_{wrong}$            & 62.10 $_{43.29}$ & 34.17 & 48.79 & \\
\hline
%\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{5}{l}{English$\rightarrow$German} \\
\hline
$Mixed$                        & 57.37 $_{37.94}$ & 23.10 & 63.54 & \\
\hline
$\mathtt{FT}_{EMEA}$  & 65.64$_{44.71}$ & 12.36 & 15.93 & \\
$\mathtt{FT}_{EPPS}$   & 24.90 $ $ & 22.98 & 26.26 & \\
$\mathtt{FT}_{ECB}$     & 41.80 $ $ & 15.97 & 71.07 & \\
\hline
$\mathtt{DC}$                & 62.53 $_{39.25}$ & 23.74 & 65.71 & \\
%\hline
%$\mathtt{WDCMT}$ & 64.05 $_{38.54}$ & 22.82 & 67.00 & \\
\hline
$\mathtt{LDR}_{oracle}$     & 63.43 $_{40.04}$ & 22.66 & 64.40 & \\
$\mathtt{LDR}_{oracle}^{0.5}$   & 63.27 $_{38.16}$ & 21.83 & 69.55 & \\
%$\mathtt{LDR}_{generic}$   & 63.27 $_{39.75}$ & 22.62 & 63.70 & \\
$\mathtt{LDR}_{pred}$        & 63.17 $_{39.92}$ & 22.51 & 64.00 & \\
$\mathtt{LDR}_{wrong}$     & 56.84 $_{37.05}$ & 22.06 & 61.66 & \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BLEU scores for RNN systems\label{tab:results-rnn}}
\end{table}
% \clearfloat

@@

\begin{table}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|c|}
\hline
Model & EMEA & EPPS & ECB & Avg. \\
\hline
%\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{5}{l}{English$\rightarrow$French} \\
\hline
$\mathtt{LDR}_{pred}^{condgru}$  & 71.70 $_{46.21}$ & 35.09 & 51.22 & \\
$\mathtt{WDCMT}$           & 68.76 $_{45.29}$ & 35.71 & 52.75 & \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BLEU scores for RNN systems. Comparison between a version of $\texttt{LDR}_{pred}$ using conditional GRUs and \texttt{WDCMT}.\label{tab:results-rnn-wdcmt}}
\end{table}

@@

\subsection{Balancing generic and domain-specific representations\label{secc:region_size}}

@@

\begin{table}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|c|}
\hline
$\mathtt{LDR}_{oracle}$ & EMEA & EPPS & ECB & Avg. \\
\hline
\multicolumn{5}{l}{English$\rightarrow$French} \\
\hline
 size=4   & 74.65 $_{49.61}$ & 37.42 & 54.49 & \\
 size=8   & 74.26 $_{49.90}$ & 37.67 & 54.07 & \\
 size=16 & 74.15 $_{49.10}$ & 37.78 & 54.56 & \\
 size=32 & 75.10 $_{48.61}$ & 37.64 & 54.29 & \\
 size=64 & 74.50 $_{50.17}$ & 37.27 & 54.50 & \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BLEU scores for the Transformer architecture for varying domain-specific embedding sizes \label{tab:embedding-size}}
\end{table}

@@

As expected, a huge gap is observed over the IT test set when learning includes in-domain data.
Note that $\mathtt{LDR}_{oracle}^*$ clearly outperforms $\mathtt{Mixed}^*$ by a large margin over the IT test set.
%
Considering the other test sets: both models similarly enhance their performance on the ECB test set;
$\mathtt{LDR}_{oracle}^*$ shows gains over the EMEA test set while a loss of quality is observed on $\mathtt{Mixed}^*$;
using IT data does not impact the quality of translations of the EPPS test set of any of the models.
Overall better results are obtained by our $\mathtt{LDR}_{oracle}$ model when trained including the additional domain dataset.
Thus, confirming the ability of the model to easily integrate new domains. % as supplementary training data becomes available.
%New domains are easily integrated in the model if the corresponding embedding regions are reserved in advance.

>>>>

\begin{table}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|lcc|c|}
\hline
Model & EMEA & EPPS & ECB & Avg. \\
\hline
%\multicolumn{8}{l}{} \\[-9pt]  
\multicolumn{5}{l}{English$\rightarrow$French} \\
\hline
$\mathtt{Mixed}$          & 67.69$_{47.60}$ & 37.50 & 53.49 & \\
\hline
$\mathtt{FT}_{EMEA}$ & 76.77$_{49.43}$ & 17.16 & 11.99 &\\
$\mathtt{FT}_{EPPS}$  & 20.86 & 37.04 & 24.53 &  \\
$\mathtt{FT}_{ECB}$    & 26.93 & 27.09 & 56.52 & \\
\hline
$\mathtt{DC}$              & 67.87$_{45.42}$ & 37.31 & 54.14 & \\
\hline
$\mathtt{LDR}_{oracle}$            & 74.26$_{49.90}$ & 37.67 & 54.07 & \\
$\mathtt{LDR}_{oracle}^{0.5}$   & 74.95$_{49.38}$ & 37.35 & 55.91 & \\
%$\mathtt{LDR}_{generic}$          & 73.97$_{49.54}$ & 37.81 & 53.67 & \\
$\mathtt{LDR}_{pred}$               & 74.29$_{49.84}$ & 37.73 & 54.01 & \\
$\mathtt{LDR}_{wrong}$            & 72.95$_{49.78}$ & 37.62 & 53.35 & \\
  \hline
%\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{5}{l}{English$\rightarrow$German} \\
\hline
$\mathtt{Mixed}$         & 64.57$_{42.99}$ & 26.47 & 68.67 & \\
\hline
$\mathtt{FT}_{EMEA}$ & 68.35$_{42.97}$ & 17.02 & 32.87 & \\
$\mathtt{FT}_{EPPS}$  & 36.19 & 26.29 & 40.71 & \\
$\mathtt{FT}_{ECB}$   & 24.72 & 18.36 & 74.05 & \\
\hline
$\mathtt{DC}$ & 63.48$_{42.98}$ & 26.27 & 66.95 & \\
\hline
$\mathtt{LDR}_{oracle}$ & 70.90$_{46.12}$ & 26.30 & 68.90 & \\
$\mathtt{LDR}_{oracle}^{0.5}$ & 71.31$_{45.23}$ & 25.98 & 73.74 & \\
%$\mathtt{LDR}_{generic}$ & 70.86$_{45.60}$ & 26.14 & 68.59 & \\
$\mathtt{LDR}_{pred}$ & 70.89$_{46.12}$ & 26.53 & 68.63 & \\
$\mathtt{LDR}_{wrong}$ & 69.51$_{43.50}$ & 26.31 & 66.86 & \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BLEU scores for  Transformer systems \label{tab:results-trsf}}
\end{table}

\begin{table}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|lcc|c|}
\hline
Model & EMEA & EPPS & ECB & Avg. \\
\hline
%\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{5}{l}{English$\rightarrow$French} \\
\hline
$Mixed$                         & 65.42$_{45.11}$ & 34.70 & 51.38 & \\
\hline
$\mathtt{FT}_{EMEA}$   & 72.06$_{47.33}$ & 18.62 & 16.78 & \\
$\mathtt{FT}_{EPPS}$    & 35.47$ $ & 34.61 & 39.56 & \\
$\mathtt{FT}_{ECB}$      & 21.93$ $ & 22.60 & 51.53 & \\
\hline
$\mathtt{DC}$                            & 68.26$_{43.76}$ & 35.13 & 50.09 & \\
% \hline
%$\mathtt{WDCMT}$           & 68.76$_{45.29}$ & 35.71 & 52.75 & \\
\hline
$\mathtt{LDR}_{oracle}$            & 71.73$_{46.30}$ & 35.21 & 50.91 & \\
%$\mathtt{LDR_{condgru}}_{pred}$   & 71.7$_{46.21}$ & 35.09 & 51.22 & \\
$\mathtt{LDR}_{oracle}^{0.5}$   & 71.70$_{46.41}$ & 34.24& 52.37 & \\
%$\mathtt{LDR}_{generic}$          & 70.59$_{46.37}$ & 35.22 & 49.68 & \\
$\mathtt{LDR}_{pred}$               & 72.76$_{46.35}$ & 35.10 & 50.38 & \\
$\mathtt{LDR}_{wrong}$            & 62.10$_{43.29}$ & 34.17 & 48.79 & \\
\hline
%\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{5}{l}{English$\rightarrow$German} \\
\hline
$Mixed$                        & 57.37$_{37.94}$ & 23.10 & 63.54 & \\
\hline
$\mathtt{FT}_{EMEA}$  & 65.64$_{44.71}$ & 12.36 & 15.93 & \\
$\mathtt{FT}_{EPPS}$   & 24.90$ $ & 22.98 & 26.26 & \\
$\mathtt{FT}_{ECB}$     & 41.80$ $ & 15.97 & 71.07 & \\
\hline
$\mathtt{DC}$                & 62.53$_{39.25}$ & 23.74 & 65.71 & \\
%\hline
%$\mathtt{WDCMT}$ & 64.05$_{38.54}$ & 22.82 & 67.00 & \\
\hline
$\mathtt{LDR}_{oracle}$     & 63.43$_{40.04}$ & 22.66 & 64.40 & \\
$\mathtt{LDR}_{oracle}^{0.5}$   & 63.27$_{38.16}$ & 21.83 & 69.55 & \\
%$\mathtt{LDR}_{generic}$   & 63.27 $_{39.75}$ & 22.62 & 63.70 & \\
$\mathtt{LDR}_{pred}$        & 63.17$_{39.92}$ & 22.51 & 64.00 & \\
$\mathtt{LDR}_{wrong}$     & 56.84$_{37.05}$ & 22.06 & 61.66 & \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BLEU scores for RNN systems\label{tab:results-rnn}}
\end{table}
% \clearfloat

@@

\begin{table}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|c|}
\hline
Model & EMEA & EPPS & ECB & Avg. \\
\hline
%\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{5}{l}{English$\rightarrow$French} \\
\hline
$\mathtt{LDR}_{pred}^{condgru}$  & 71.70$_{46.21}$ & 35.09 & 51.22 & \\
$\mathtt{WDCMT}$           & 68.76$_{45.29}$ & 35.71 & 52.75 & \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BLEU scores for RNN systems. Comparison between a version of $\texttt{LDR}_{pred}$ using conditional GRUs and \texttt{WDCMT}.\label{tab:results-rnn-wdcmt}}
\end{table}

@@

\subsection{Balancing generic and domain representations\label{secc:region_size}}

@@

\begin{table}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|c|}
\hline
$\mathtt{LDR}_{oracle}$ & EMEA & EPPS & ECB & Avg. \\
\hline
\multicolumn{5}{l}{English$\rightarrow$French} \\
\hline
 size=4   & 74.65$_{49.61}$ & 37.42 & 54.49 & \\
 size=8   & 74.26$_{49.90}$ & 37.67 & 54.07 & \\
 size=16 & 74.15$_{49.10}$ & 37.78 & 54.56 & \\
 size=32 & 75.10$_{48.61}$ & 37.64 & 54.29 & \\
 size=64 & 74.50$_{50.17}$ & 37.27 & 54.50 & \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BLEU scores for the Transformer architecture for varying domain-specific embedding sizes \label{tab:embedding-size}}
\end{table}

@@

As expected, a huge gap is observed over the IT test set when learning includes in-domain data.
Note that on this test set $\mathtt{LDR}_{oracle}^*$ clearly outperforms $\mathtt{Mixed}^*$ by a large margin.
%
Considering the other test sets: both models similarly enhance their performance on the ECB test set;
$\mathtt{LDR}_{oracle}^*$ shows gains over the EMEA test set while a loss of quality is observed on $\mathtt{Mixed}^*$;
using IT data does not impact the quality of translations of the EPPS test set of any of the models.
Overall better results are obtained by our $\mathtt{LDR}_{oracle}$ model when trained including the additional domain dataset.
Thus, confirming the ability of the model to easily integrate new domains. % as supplementary training data becomes available.
%New domains are easily integrated in the model if the corresponding embedding regions are reserved in advance.
